---
title: "![](armour.svg) Notes - DM ONLY!"
output:
  html_document:
      toc: yes
      toc_float: yes
      theme: readable
---

```{r global_options, include=F}
knitr::opts_chunk$set(eval=F)
```

```{r eval=F, include=F}
# Dependencies

library(rmarkdown)
library(knitr)
```

Session log

Action summaries

* construct experimentation methodolgy as mechanism for puzzle solving
* teleportation circles

* NPCs needed
    + leader of local hero's union
    + cell leader for emerald compact

## Session Notes {.tabset .tabset-fade}

### Current

#### Previous Summary

NA

#### Game Dates
* **Start:** 3rd day of Kythorn (The Time of Flowers)
* **End:**

#### NPCs Present
*

#### Location(s)
*

#### General Loot
*

#### Plot Hooks
*

#### UA NPCs
*

#### UA Encounters
*

#### Session Events
*

---

### Template

#### Previous Summary

NA

#### Game Dates
* **Start:**
* **End:**

#### NPCs Present
*

#### Location(s)
*

#### General Loot
*

#### Plot Hooks
*

#### UA NPCs
*

#### UA Encounters
*

#### Session Events
*

---

### 0

My job as DM:

* Success as a DM
    + is delivering narrative depth, game realism, and player reward through process. Winning does not take a binary form in DnD. Those can be player goals as well. 
* Specifics of my job as DM
    + I am the god of this world, but my purpose is to be an impartial narrator and referee. When I use discretion, it will always be in the larger interest of the above stated goals.
    + There will routinely be game knowledge I need but don't posses in the moment. As a result, I will be constantly thinking of the cost-benefit of how difficult it would be to address the lacking info. If it's prohibitive, I will make a judgement and note I need to clarify post-session.
* I will generally be hands off.
* The story may be fragmented.
    + and things may feel clunky and we may ultimately never complete major arcs. My job is to guide the game in a manner that is adaptive to the direction, momentum, and needs of the party.

Your job as players:

* Participate in the creation of the world.
    + There are times I may call on you to do this. There are times you will be totally unaware your actions spurred unplanned events. You are just as vital as the DM to the creation of the narrative.
* Embrace the suspension of disbelief.
    + Avoid metagame awareness by compartmentalizing knowledge and working through mechanisms that make sense for your char.
* Personify your char as much as possible.
    + Aim for maximum cognitive immersion. DnD is unique in the level of mental access you have to connect with and guide the actions of a char. Strengths are obviously emphasized, but flaws hold relevance too.
* Cheating or buffing gameplay holds no value.
    + Meaningful party outcomes, good or bad, are where success is had. As the players of dwarf fortress say, "losing is fun". Get out of the "beowulf" mindset (success is automatic and always assumed).
* Cheating in-character definitely holds value
    + but it should make sense. For instance, a CN type would be out of character only doing good natured things. Steal from the party, murder every hobo, just do it with broad consideration for relevance and impact.
* Talking about success
    + it includes the thoughts and preferences of each party member. If something makes you uncomfortable, if there is an aspect of game play you'd like to see elevated or diminished, raise these issues as we go.

---

### 0627

---

## Tools

### Tables

* [DM Tables](https://dungeonmastertools.github.io/)
    + Player ref sheet
    + Treasure tables
    + Magic Items tables
    + Travel
* [donjon](https://donjon.bin.sh/5e/)
    + Spell sheet
    + Enc table
    + Shop generator
    + Dungeon generator

### PCs

* [Ashitaka](https://www.dndbeyond.com/characters/30354523) (Chang)
* [Dimaya Urtac](https://www.dndbeyond.com/characters/30130370/FlOc6M) (Olson)
* [Sk&auml;gd&umacr;n](https://www.dndbeyond.com/characters/30600024/vTJOE5) (Skoglund)
* [Uzi Soggybottom](https://www.dndbeyond.com/characters/30350744/bpyqUe) (Gervais)
* [Vaer&uuml;ne](https://www.dndbeyond.com/characters/29959151/Hd5Mwh) (Spaeth)

---

## Chars

<details>

  <summary>**Template**</summary>

* **Race:**
* **Class:**
* **Motivations:**
* **Traits:**
* **Location:**
* **Background:**

</details>
<br />

### UA NPCs
* npc bard named onry strong sense of nationalism

### Leo Ferrari
* **Race:**
* **Class:**
* **Motivations:**
* **Traits:**
* **Location:**
* **Background:**

### Prahmethoth
* **Race:** Alhoon
* **Class:**
* **Motivations:**
* **Traits:**
* **Location:**
* **Background:**

### Farmer
* **Race:**
* **Class:**
* **Motivations:** Live a simply after a life of adventuring
* **Traits:** old, feeble
* **Location:** Farm off main road south of Holworth.
* **Background:** Spent a career as an adventurer but has since retired.


### W. Fitzhugh Brundage
* **Race:**
* **Class:**
* **Motivations:** discovery, aid the party in pursuit of discovery, support Progenitor Trust
* **Traits:** intelligent, curious, persistent
* **Location:** Threapnalt University
* **Background:**
    + Conducts academic work on the arcane.
    + Stands as a leader in the early findings of arcane mechanisms (Ves-Tonder System).
    + Currently expanding into area of esoteric drift.
    + Is an active member of the Progenitor Trust.

### Mule
* **Race:**
* **Class:**
* **Traits:** feeble, psynic abilities, appears to be harmless
* **Motivations:** serve BBG as main lieutenant
* **Location:**
* **Background:**

---

## Encounters

<details>

  <summary>**Template**</summary>

* **Dungeon map:**
* **Combat map:**
* **Location:**
* **Weather:**
* **Environment:**

</details>
<br />

puzzle ideas

* poem that is a for loop to complete task
* backward wall - wall appears when party turns around. cryptic enscription indicating they need to walk backward to go forward
* rude door
* items dissappear, task completed without equipment
* prisoners dilemma - players enter room where they respectively enter visual\/audio cones of isolation. must figure out dynamic collectively to solve puzzle
    + players role covert int saves
    + split party in half to seperately meet the king
    + king explains they've been selected for their intelectual and strategic prowess and brought to his "strategic plane" (think of better term for situation room)
    + king states he is in need of guidance on how to spend resources in his kingdom for the next 3 yrs relative to his neighboring rival
    + he can invest in his kingdom or go to war
    + should he prepare for peace or prepare for war
    + players receive payment for lucrative guidance and punishment for lopsided outcomes.
* pc performs action to bind themselves to curse, they get isolated, a simulacrum of that pc returns to the party to fight them
* hoffman encoding for BBG encrypted messages
* graph algorithm
* timed effects
* kobe - party needs to cast fireball through basketball hoop
* https:\/\/docs.google.com\/document\/d\/1hfompGbslrV_YvQ4ktPnY7vg-_blkIZ72hPcXLEWZdQ\/edit

---

## Organizations

<details>

  <summary>**Template**</summary>

* **Description:**
* **Mission statement:**
* **Motto:**
* **Goals:**
* **Location:**
* **Services:**
* **Membership:**
* **NPCs:**
* **Story arcs:**
* **Background:**

</details>
<br />

### Round Earth Society
* **Description:** An advocacy group that promotes the belief the world is spherical while denying existence of a firmament.
* **Mission statement:**
* **Motto:** We're ahead of the curve.
* **Goals:** Promote the belief that the world is spherical.
* **Location:**
* **Services:**
* **Membership:**
* **NPCs:** Leo Ferrari
* **Story arcs:**
* **Background:** This group is one of many elements who have embraced psuedointellectual leanings in the wake of the Awakening. The degree to which society's understanding of reality was fundamentally changed has uprooted many previously steadfast beliefs.

### Progenitor Trust
* **Description:** An order of Verdan mages who, previously beset by oppression, heavily embraced magic post-[awakening].
* **Mission statement:**
* **Motto:**
* **Goals:** Employ academic head start in magic prowess to organize a coup. Upon seizing power, embark on aggressive conquest in expansion of race influence.
* **Location:** Threapnalt University
* **Services:**
* **Membership:**
* **NPCs:**
    + W. Fitzhugh Brundage
* **Story arcs:**
    + Realignment
* **Background:** The race are a people who have historically been oppressed by the ruling class of their locale. In the immediate aftermath of the [awakening], the race made early investments in magical knowledge and building of their collective capability. A race previously beset with little opportunity saw dramatic advancements in the state of their human capital. Even still, this did not come with social realignment, and thus, the leadership of the race have set out to correct this historic imbalance.

### Emerald Compact
* **Description:** Underground, decentralized eco-terrorist group that utilizes militant tactics in limiting humanoid environmental impact.
* **Mission statement:**
* **Motto:** The earth laughs in flowers
* **Goals:**
    + Enlists agents to support their cause of environmental intervention.
    + Coordinate efforts to obstruct humanoid causes of environmental damage by any means necessary.
    + A primary target of their focus is the recent expansion in mining for magical ore.
* **Location:** Unknown
* **Services:**
* **Membership:**
    + Allegiance is sworn upon receiving an invitation to become an agent.
    + Agents are conscripted to secrecy.
    + All druids are given an opportunity at membership.
* **NPCs:**
* **Story arcs:**
* **Background:**

### Hero’s Alliance
* **Description:** A union of adventuring members with common goals and public professional services.
* **Mission statement:**
* **Motto:** I wish to see what lies beyond
* **Goals:**
    + Provide public access to adventurer talent and services through contract hire.
    + Serve as support union for adventurers.
    + Give endless feed of easy quest plot hooks.
    + Remain apolitical.
* **Location:** Branches in most major cities.
* **Services:**
    + Contract to hire adventurer jobs
    + Training
    + Practice combat theater
* **Membership:**
    + Must be actively working as a professional adventurer.
    + Complete a test job at discretion of branch warden
* **NPCs:**
* **Story arcs:**
    + An introduction
* **Background:**

### Snail Mail
* **Description:** [world name] Distributed Messaging Brokerage. A communication service of the flail snail hive mind collective. AKA Snail Mail.
* **Mission statement:**
* **Motto:**
* **Goals:** Provide high fidelity messaging services across the realm.
* **Location:** Branches in most major cities.
* **Services:**
    + Priority Telepathy –
    + Priority Express Telepathy -
    + Beacon License – recipients receive charm which allows for persistent tracking in roaming message delivery.
    + Joke payment – flail snails love jokes. A new joke (and food) can substitute as payment for a received message.
* **Membership:**
    + Standard pricing array for varying services
    + Certain Licenses that allow for elevated access and pricing gratuity
* **NPCs:** flail snail hive mind collective
* **Story arcs:** An introduction
* **Background:** Flail snails take their service to the realm very seriously. Their collective psionic capabilities allowed them to provide their services long before the [awakening] and the introduction of other methods of arcane data transfer.

### Threapnalt University
* **Description:** An institution of higher learning in the arcane arts
* **Mission statement:**
* **Motto:** Driven to Discover
* **Goals:** Advance the discovery of arcane knowledge.
* **Location:** Holworth, Noon Orchard district
* **Services:**
    + Library
    + Training
* **Membership:**
    + Admissions process for students
    + Hiring process for faculty
* **NPCs:**
    + W. Fitzhugh Brundage
* **Story arcs:**
    + Main plot
    + Realignment
* **Background:** Named for founding leader of Progenitor Trust.

---

## Places

<details>

  <summary>**Template**</summary>

* **Location:**
* **Description:**
* **NPCs:**
* **Organizations:**
* **Items:**
* **Story arcs:**
* **Background:**

</details>
<br />

---

## Story arcs

<details>

  <summary>**Template**</summary>

* **Outline:**
    + Event:
    + Impact:
    + Call to action:
    + Turn:
    + Resolution:
* **Exposition:**
* **Items:**
* **Chars:**
* **Plot hooks:**  
* **Events:**
    + Anticipated:**
    + Transpired:**

</details>
<br />


https://docs.google.com/document/d/1ADbrYtsI6_EhYRgBtzKQB1Iv4TgbouZfLKV7YRU2XeM/edit

With esoteric drift:

* The realm lacks magical properties due to an arcane energy void
* BB identifies the value of this to advance arcane study and avoid elder brain detection while pursuing motivations
* BB discovers method to manipulate esoteric drift that fills arcane void, making interaction with the weave possible
* Need: ability or artifact to manipulate esoteric drift.
* This artifact/ability gives BB ability to conduct work in synthesized arcane space, effectively turning magic on/off. Goal is to achieve some kind of immortality without elder brain (lichdom, divinity)
* Party can discover method of controlling ability or forging artifact to give esoteric drift permanence.

subplots

political factions of mage guild

* order of thieves - secretly enlist party thief as plot mechanism
* construct experimentation methodolgy as mechanism for puzzle solving
* create historian character to provide exposition on discovery of magic
* create university and academic chars to provide exposition on magical properties
* subjegated race embraces magic early and forms strong fabric within magic community at heart of country where magic is introduced. they intend to over throw their oppressors and embark on aggressive conquest.
* radical environmentalist group forms and enlists agents to support their cause of intervention
* mining for magical ore has expanded dramatically
* [world name] distributed messaging brokerage - A service of the flail snail hive mind collective. party receives credentials for premium beacon \"tracking\" service. snails take payment in food or jokes.
* create npc modeled after the mule. feeble, psyonic abilities, appears to be harmless. maybe is main lieutenant for BBG.
* gods converge on the reintroduction of magic, sending heralds and trying to vie for control of \"fresh\" territory.
* arms manufacturer offers lucrative contract to party

### Cows in the village

### HA Contracts
* Bandits have overrun a nearby holy site and captured priest.
    + Obj: Clear the site, and free priest.
    + Pay:
* A monster is making travel dangerous to the NE.
    + Obj: Eliminate monster. Return with proof.
    + Pay:
* A local smith is experiencing daily vandalism.
    + Obj: Stand watch for night to deal with vandals.
    + Pay:
* A territorial dispute between merchant guilds has led to bouts of violence.
    + Obj: Mediate terms. Address any non-compliance.
    + Pay:
* A minning operation is experiencing insurrection among its workforce.
    + Obj: Infiltrate the operation and eliminate sedition leadership.
    + Pay:
* A noble is in need of an escort.
    + Obj: Act as guide and defense for noble's detail
    + Pay:
* Something with the university
* Recent evidence of an assumed lost family heirloom has surfaced.
    + Obj: Confer with client, and retrieve item.
    + Pay:
* A farmer outside of town is experiencing a giant wolf spider infestation.
    + Obj: Inspect property, and eliminate [monsters].
    + Pay:
* The activity of a kobold stronghold has begun to encroach on the neighboring hamlet.
    + Obj: Clear stronghold. Destroy any stronghold infrastructure.
    + Pay:
* A dragon hatchling has been discovered in the countryside.
    + Obj: Venture to its nest and eliminate it before it becomes a major liability
    + Pay:

Join a banner to fight in Challenger Guantlet

* EVENT: main villan introduces magic to realm
* MOTIVATION: his realm is failing. player realm contains resource that sustains magic with his influence. entering player realm allows him to continue magical work (become divinity or something)
* PLAYER CHOICE: recieve benefits of magic at the expense of authoritarian/theocratic rule under villan or eliminate villan and lose magic.
* PLAYER DISCOVERY: identify method to sustain resource independently and weaken villan.
* PLAYER GOAL: enable resource. defeate villan.

### A Titan's Price
* **Outline:**
    + *Event:* Prahmethoth introduces magic to realm.
    + *Impact:* After millennia without arcane magic, this world undergoes a dramatic technilogical awakening.
    + *Call to action:* Inconsistencies in magical fidelity and a growing presence of Prahmethoth's work begin impacting society.
    + *Turn:* Upon initial confrontation, the PCs learn Prahmethoth has granular control of the arcane weave, rendering him virtually invincible.
    + *Resolution:* The PCs attempt to develop a method for esoteric permanence, allowing them to fight Prahmethoth at full strength.
* **Exposition:** This world is a lost Plagueland where a fundamental connection with the weave is broken. Due to unknown effects, esoteric drift dynamics have effectively created an arcane energy void. All mechanics of the Ves-Tonder system are intact but cannot function with the energy vacany. While attempting to attain a level of divinity, the Alhoon Prahmethoth travels to this realm in an effort to avoid detection from the Elder Brain. Through his work, he discovers a method to manipulate esoteric drift. This enables the draw of arcane energy to this space, effectively introducing the completed circuit of the weave to the realm.
* **Items:**
* **Chars:**
    + Prahmethoth
* **Plot hooks:**  
* **Events:**
    + Anticipated:**
        - "blackout" event where magic shuts off momentarily. BBG is testing something that impacts esoteric permanence.
    + Transpired:**

### Heralds Inbound
* **Outline:**
    + *Event:* gods converge on the reintroduction of magic, sending heralds and trying to vie for control of "fresh" territory.
    + *Impact:*
    + *Call to action:*
    + *Turn:*
    + *Resolution:*
* **Exposition:**
* **Items:**
* **Chars:**
* **Plot hooks:**  
* **Events:**
    + Anticipated:**
    + Transpired:**

### An Introduction
* **Outline:**
    + *Event:* PCs appear and witness farm being attacked.
    + *Impact:* Risk of harm to everyone in area.
    + *Call to action:* Only the party can save the farmer.
    + *Turn:* Party decides to intervene.
    + *Resolution:* Farmer is grateful and passes on prized adventuring items
* **Exposition:** The PCs were drawn to Holworth as the cultural epicenter of magic. The farmer is a former adventurer and will pass on his items if assisted.
* **Items:** ArcReader, Snail Mail beacon license, Hero’s Alliance contract
* **Chars:**
    + Old farmer
    + Attacking giant wolf spiders
* **Plot hooks:**  NA
* **Events:**
    + Anticipated:**
        - Random encounter with aggressor NPCs
        - Party intervenes to save farmer
        - Party carries on to investigate leads from items they received
    + Transpired:**

### Realignment
* **Outline:**
    + *Event:* The Progenitor Trust attempts to organize a coup and seize power within their locality.
    + *Impact:* With their early investments in magical capability, the Trust is able to upend the historical power structure and seek greater ambitions (conquest).
    + *Call to action:* 1) Gain sympathy of party and participate in the coup. 2) Prevent coup.
    + *Turn:* 1) Party becomes aware of intentions beyond coup
    + *Resolution:* Party succeeds in either C2A they choose.
* **Exposition:** The race are a people who have historically been oppressed by the ruling class of their locale. In the immediate aftermath of the [awakening], the race made early investments in magical knowledge and building of their collective capability. A race previously beset with little opportunity saw dramatic advancements in the state of their human capital. Even still, this did not come with social realignment, and thus, the leadership of the race have set out to correct this historic imbalance.
* **Items:**
* **Chars:**
* **Plot hooks:** 
* **Events:**
    + Anticipated:**
        - Party interacts with race leadership.
        - Blackout creates window for local leader to raid race hq.
        - Coup succeeds and race installs new power structure.
        - Race begins expansion of forces in effort to embark on aggressive conquest
    + Transpired:**


### Arms Race
* **Outline:**
    + *Event:* arms manufacturer offers lucrative contract to party
    + *Impact:*
    + *Call to action:*
    + *Turn:*
    + *Resolution:*
* **Exposition:**
* **Items:**
* **Chars:**
* **Plot hooks:**  
* **Events:**
    + Anticipated:**
    + Transpired:**

### Twin Metals
* **Outline:**
    + *Event:* mining for magical ore has expanded dramatically
    + *Impact:*
    + *Call to action:*
    + *Turn:*
    + *Resolution:*
* **Exposition:**
* **Items:**
* **Chars:**
* **Plot hooks:**  
* **Events:**
    + Anticipated:**
    + Transpired:**

---

## Things

<details>

  <summary>**Template**</summary>

* **Qualities:**
* **Location:**
* **Background:**

</details>
<br />

ArcReader, Snail Mail beacon license

