---
title: "![](armour.svg) DM Screen - DM ONLY!"
output:
  html_document:
      toc: yes
      toc_float: yes
      theme: readable
---

```{r global_options, include=F}
knitr::opts_chunk$set(eval=F)
```

```{r eval=F, include=F}
# Dependencies

library(rmarkdown)
library(knitr)
```

## Session Notes

#### Previous Summary
* The party accepted another HA contract that will take them through the wilderness at the behest of a local noble business leader.
* In initiating this contract, the party met Lady Luna Laurentz and her CoS, Onry. They set out west toward the mine, first traveling down the roard toward Marwark.
* During this leg of the journey, the party discovers they are being tracked by a lone Orog who they ambush and dispatch with some effort.

#### Starting Conditions
* **Start:** 5th day of Kythorn (The Time of Flowers)
* **End:**
* **Weather:** clear, 9mph, 56
* **Location(s):**
    + *Start:* Campsite just NE of Marwark
* **NPCs:**
    - Lady Luna
    - Onry
* **Circumstances:**
    + The party had just finished a battle and was nearing EoD. They have just begun a long rest.

#### Session Events

**Anticipated**

* The party will continue on their journey toward the Laurentz mine.
* At some point, they will be attacked by a unit Progenitor Trust mages who want to interogate Lady Luna.
* In an effort to avoid bloodshed and deter the party from accomplishing their goal, the PT mages will send the party to a puzzle filled pocket dimension.

**Occurred**

*

---

### UA Content

*Plot Hooks*

1. A horde of giants has destroyed an abandoned outpost to the southwest.
2. A gathering of craftsmen was murdered on the road to the northwest.
3. An army of dwarves stumbled into a hidden section of the sewers.
4. A band of entertainers is on the run from the law for a crime they didn't commit.
5. A troupe of wanderers is looking to buy strange devices that can be found beneath the mountains far to the south.

*Random Encounters*

<details>
  <summary>**Savanna - Hill**</summary>

1. 2 x Meazel (cr 1, mtf 214); deadly, 400 xp; treasure 16 cp + 22 cp
1. 1 x Deinonychus (cr 1, vgm 139); easy, 200 xp; treasure 13 cp
1. Nilbog (cr 1, vgm 182) and 1 x Goblin (cr 1/4, mm 166); medium, 250 xp; treasure 8 gp + 20 cp
1. 2 x Meazel (cr 1, mtf 214); deadly, 400 xp; treasure 7 gp + 12 sp
1. 1 x Griffon (cr 2, mm 174); hard, 450 xp; treasure 20 cp
1. 2 x Half-ogre (cr 1, mm 238); deadly, 400 xp; treasure 17 cp + 13 sp
1. 1 x Gnoll Flesh Gnawer (cr 1, vgm 154); easy, 200 xp; treasure 11 ep
1. 1 x Berserker (cr 2, mm 344); hard, 450 xp; treasure 12 gp
1. Goblin Boss (cr 1, mm 166) and 2 x Goblin (cr 1/4, mm 166); deadly, 300 xp; treasure 8 sp + 17 sp + 8 ep
1. Nilbog (cr 1, vgm 182) and 1 x Goblin (cr 1/4, mm 166); medium, 250 xp; treasure 11 cp + 9 ep

</details>

<details>
  <summary>**Grassland**</summary>

1. 1 x Giant Hyena (cr 1, mm 326); medium, 200 xp; treasure 11 gp
1. 1 x Deinonychus (cr 1, vgm 139); medium, 200 xp; treasure 13 sp
1. Hobgoblin (cr 1/2, mm 186) and 3 x Goblin (cr 1/4, mm 166); deadly, 250 xp; treasure 15 gp + 14 cp + 10 ep + 16 cp
1. 1 x Gnoll Flesh Gnawer (cr 1, vgm 154); medium, 200 xp; treasure 4 pp
1. 3 x Giant Goat (cr 1/2, mm 326); deadly, 300 xp; treasure 18 sp + 9 ep + 11 gp
1. 1 x Hobgoblin Iron Shadow (cr 2, vgm 162); hard, 450 xp; treasure 13 cp
1. 1 x Orc (cr 1/2, mm 246) and 1 x Ogre (cr 2, mm 237); deadly, 550 xp; treasure 20 cp + 17 cp
1. 1 x Rhinoceros (cr 2, mm 336); hard, 450 xp; treasure 19 cp
1. 3 x Worg (cr 1/2, mm 341); deadly, 300 xp; treasure 18 cp + 13 sp + 20 cp
1. 2 x Deinonychus (cr 1, vgm 139); deadly, 400 xp; treasure 8 sp + 15 sp

</details>

<details>
  <summary>**Coastal - Tropical**</summary>

1. Pseudodragon (cr 1/4, mm 254) and 4 x Pixie (cr 1/4, mm 253); deadly, 250 xp; treasure 16 gp + 11 gp + 19 cp + 14 gp + 12 cp
1. 2 x Giant Toad (cr 1, mm 329); deadly, 400 xp; treasure 16 cp + 16 cp
1. 2 x Harpy (cr 1, mm 181); deadly, 400 xp; treasure 8 gp + 7 sp
1. 1 x Tortle Druid (cr 2, mtf 242) and 1 x Tortle (cr 1/4, mtf 242); deadly, 500 xp; treasure 21 cp + 17 cp
1. 3 x Dimetrodon (cr 1/4, vgm 139); medium, 150 xp; treasure 23 cp + 8 sp + 10 sp
1. 1 x Berserker (cr 2, mm 344); hard, 450 xp; treasure 9 gp
1. 2 x Giant Lizard (cr 1/4, mm 326); easy, 100 xp; treasure 2 pp + 11 sp
1. 1 x Giant Eagle (cr 1, mm 324); easy, 200 xp; treasure 9 sp
1. 4 x Giant Lizard (cr 1/4, mm 326); hard, 200 xp; treasure 16 gp + 11 gp + 11 gp + 11 gp
1. 2 x Skulk (cr 1/2, mtf 227); medium, 200 xp; treasure 11 sp + 9 sp

</details>

<details>
  <summary>**Urban**</summary>

1. 2 x Warhorse (cr 1/2, mm 340); medium, 200 xp; treasure 8 gp + 22 cp
1. 2 x Warhorse (cr 1/2, mm 340); medium, 200 xp; treasure 15 sp + 21 cp
1. 2 x Skulk (cr 1/2, mtf 227); medium, 200 xp; treasure 15 cp + 21 sp
1. 3 x Swarm of Insects (cr 1/2, mm 338); deadly, 300 xp; treasure 12 sp + 12 gp + 12 gp
1. 1 x Yuan-ti Pureblood (cr 1, mm 310); easy, 200 xp; treasure 19 cp
1. 1 x Gargoyle (cr 2, mm 140); hard, 450 xp; treasure 10 sp
1. 3 x Giant Wasp (cr 1/2, mm 329); deadly, 300 xp; treasure 14 gp + 14 sp + 15 gp
1. 1 x Meenlock (cr 2, vgm 170); hard, 450 xp; treasure 15 gp
1. 3 x Warhorse (cr 1/2, mm 340); deadly, 300 xp; treasure 12 ep + 9 gp + 8 gp
1. 2 x Thug (cr 1/2, mm 350); medium, 200 xp; treasure 7 ep + 8 ep

</details>

<details>
  <summary>**Forest - Temperate**</summary>

1. Gnoll Pack Lord (cr 2, mm 163) and 1 x Gnoll (cr 1/2, mm 163); deadly, 550 xp; treasure 17 cp + 16 cp
1. 1 x Quickling (cr 1, vgm 187); easy, 200 xp; treasure 16 gp
1. 1 x Meenlock (cr 2, vgm 170); hard, 450 xp; treasure 23 cp
1. 2 x Giant Wasp (cr 1/2, mm 329); medium, 200 xp; treasure 13 sp + 17 cp
1. 2 x Vine Blight (cr 1/2, mm 32); medium, 200 xp; treasure 11 gp + 21 sp
1. Grung Elite Warrior (cr 2, vgm 157) and 1 x Grung (cr 1/4, vgm 156); deadly, 500 xp; treasure 11 gp + 12 gp
1. 1 x Guard Drake (cr 2, vgm 158); hard, 450 xp; treasure 12 gp
1. 1 x Orog (cr 2, mm 247); hard, 450 xp; treasure 16 sp
1. 1 x Yuan-ti Pureblood (cr 1, mm 310); easy, 200 xp; treasure 24 cp
1. 2 x Swarm of Insects (cr 1/2, mm 338); medium, 200 xp; treasure 18 cp + 19 sp

</details>

---

**Names**

* **Elfs**: Arbelladon Yinwarin , Ailas Omajyre , Alluin Balmys , Theodred Aralana , Taleasin Vasandoral , Gormar Farbalar , Ornthalas Virjyre , Nesterin Triswarin , Volodar Sylbella , Zaos Josatra
* **Dwarf**: Darendrog Metalstone , Skobrouth Keggrog , Varfulir Forgebuckle , Darefoid Steelbane , Huvouth Thunderforged , Vomdag Lavamaul , Nolgrarlug Shattermaul , Ararril Chaosshoulder , Joded Anvilbringer , Gotrad Snowview
* **Dragon**: poidhi, the Life Giver , tiorvaen, Protector of the Weak , chaervorth, the Gifted , bieperth, the Jealous One , tudhait, the Dark , dennian, the Puny , gaekae, the Tall , payvinteil, the Bunny Killer , xudaepheo, the Warm , uvirus, the Dragonlord
* **Dragon**: micdic , iktec , gosuph , krecshu , ~~baizax~~ , grona , roldrebuph , rocdraelo , velarciks , hoshiroz
* **Human**: rishun cinom , bhurad cukhen , birkudd Fourclaw , nibrork Silentbelly , mabram ven , kem navrosk , golvor Roughbow , murth Voiddrifter , thehvezuz michahkem , dinas muuhreft , temondesk netrotvurgu , zirlat vruvzako , ioy li , jiap chuen , uerdeanez zascudrul , venin paldurgel

---

**NPCs**

* **Onry**: Human Bard, strong sense of nationalism.
* **Loby Finell**: Female Halfling Paladin, Good. Str 15, Dex 8, Con 7, Int 11, Wis 14, Cha 16. Loby has a round face, with golden hair and brown eyes. She wears splint armor and wields a warhammer and shield.
* **Arget Courte**: Female Halfling Mercenary, CG. Str 10, Dex 12, Con 6, Int 13, Wis 10, Cha 15. Arget is tall and willowy, with auburn hair and soft gray eyes. She wears leather armor and wields a shortsword.
* **Threri**: Male Dwarf Cleric, NG. Str 9, Dex 12, Con 11, Int 9, Wis 15, Cha 15. Threri has blonde hair and hazel eyes, and a curly moustache. He wears hide armor and wields a light hammer. Threri seeks to discover the truth of his lineage.
* **Amira**: Female Halfling Peasant, NE. Str 10, Dex 9, Con 11, Int 9, Wis 8, Cha 9. Amira has thin gray hair and narrow brown eyes, and large ears. She wears simple clothing and carries a long knife. Amira is envious and deceitful.
* **Hildga**: Female Dwarf Ranger, N. Str 8, Dex 10, Con 12, Int 12, Wis 13, Cha 8. Hildga has cropped golden hair and gray eyes. She wears half plate and wields a whip and shield. Hildga is extravagant and fierce.
* **Ancin Gere**: Male Human Merchant, NG. Str 10, Dex 11, Con 10, Int 10, Wis 11, Cha 8. Ancin has thin red hair and blue eyes. He wears modest garments and a blue cloak. Ancin has an animal companion, a black cat named Ethen.
* **Zita**: Male Half-orc Priest, NG. Str 8, Dex 10, Con 9, Int 11, Wis 12, Cha 12. Zita has copper hair and blue eyes, and prominent ears. He wears well-made clothing and carries a fine stiletto. Zita secretly serves Kaveph, an ancient god of chaos.
* **Thrica**: Male Half-orc Alchemist, N. Str 9, Dex 6, Con 13, Int 10, Wis 14, Cha 8. Thrica has a narrow face, with blonde hair and bright green eyes. He wears well-made clothing and a sling of vials and potions. Thrica seeks revenge against the sister who betrayed him.
* **Ursas**: Female Gnome Scofflaw, NG. Str 8, Dex 10, Con 12, Int 11, Wis 11, Cha 10. Ursas has auburn hair and sharp amber eyes, and pointed ears. She wears sturdy clothing and several pouches hang from her belt.
* **Staga Jornidotr**: Female Dwarf Merchant, LN. Str 10, Dex 12, Con 12, Int 6, Wis 11, Cha 6. Staga is rough in appearance, with white hair and soft brown eyes. She wears plain clothing and a wide-brimmed hat. Staga has an animal companion, a gray rabbit named Bifar.

---

## Notes Log {.tabset .tabset-fade}

### 08/16

#### Previous Summary
* The party continued through the administrative center of the Temple of Purpose, clearing the site and finally confronting the Bandit Captain that had taken the priest hostage.
* After freeing the priest, he made the party aware that the eternal flame in the proscenium was the site of a miracle, bestowing healing powers. Additionally, the priest used a scroll to endow the entire party with inspiration.
* The party then returned to the Holworth HA to claim their contract and pickup a new one

#### Starting Conditions
* **Start:** 4th day of Kythorn (The Time of Flowers)
* **End:** 5th day of Kythorn (The Time of Flowers)
* **Weather:** clear, 10mph, 57F
* **Location(s):**
    + *Start:* The lobby of the Holworth HA
* **NPCs:** Asarkal
* **Circumstances:**
    + The party is in the process of accepting HA contract #8

#### Session Events

**Anticipated**

* The party will be confonted by a member of the Aldock Distributed Messaging Brokerage to update their Beacon License.
* Contract #8 will take the party to meet with Lady Luna to initiate their travel to the Laurentz Mine.

**Occurred**

* The party accepted another HA contract that will take them through the wilderness at the behest of a local noble business leader.
* In initiating this contract, the party met Lady Luna Laurentz and her CoS, Onry. They set out west toward the mine, first traveling down the roard toward Marwark.
* During this leg of the journey, the party discovers they are being tracked by a lone Orog who they ambush and dispatch with some effort.

---

### 07/26

#### Previous Summary
* The party descended on the Temple of Purpose in an effort to clear this holy site of the bandits that recently overtook it.
* They had a brush with fate as Skagdun nearly perished in confronting a set of guards in the outdoor proscenium.
* After recuperating, the party returned to the open air cathedral to enter into the bowels of the site, presumptively approaching the hostage priest. 

#### Starting Conditions
* **Start:** 4th day of Kythorn (The Time of Flowers)
* **End:** 4th day of Kythorn (The Time of Flowers)
* **Weather:** Clear, 0mph, 53F
* **Location(s):**
    + *Start:* Temple of Purpose, underground operation, rm4
* **NPCs:** Priest and bandit captain in secret rm2
* **Circumstances:**
    + The party is in rm4 of the Temple of Purpose having just defeated a bandit in the hall.
    + The first encounter was handled recklessly and may have stirred up awareness in the halls.

#### Session Events

**Anticipated**

* Recover Temple of Purpose and save priest. Priest will offer Scroll of Inspiration that provides each member of party with single bout of inspiration.
* Return to Hero’s Alliance to claim contract and pick up another. I anticipate they will go after the dragon.
* If it’s the dragon, they will find a solo silver dragon wyrmling who is non-combative and lawful good. If unprovoked, she will aid the party.
* Party will hopefully redeem snail mail license.

**Occurred**

* The party continued through the administrative center of the Temple of Purpose, clearing the site and finally confronting the Bandit Captain that had taken the priest hostage.
* After freeing the priest, he made the party aware that the eternal flame in the proscenium was the site of a miracle, bestowing healing powers. Additionally, the priest used a scroll to endow the entire party with inspiration.
* The party then returned to the Holworth HA to claim their contract and pickup a new one

---

### 07/12

#### Previous Summary

* On their journey to Holworth to take part in this era of magical awakening, the party came across a farmer’s plot and fought a collection of wolf spiders.
* Upon victory, the party conferred with the Farmer receiving a Hero's Alliance contract he had open, a Beacon license to be activated at the Snail Mail office, and the ArcReader. Ashitaka provided a tender offering of a love pillow to the farmer.
* After venturing to Holworth, the party briefly stopped by the Wonky Donkey for a drink and then traveled to claim their contract and join the Hero's Alliance.
* The party set out to complete contract #1 and ended the session outside the holy site.

#### Game Dates

#### NPCs Present
* None

#### Starting Conditions
* **Weather:** clear, wind 14mph, high 53
* **Location(s):**
    + *Start:* Temple of Purpose from HA contract #1
    +
* **Circumstances:** Setting up in LOS of holy site, preparing to attack.

#### Session Events
**Anticipated:**

* Recover Temple of Purpose and save priest. Priest will offer Scroll of Inspiration that provides each member of party with single bout of inspiration.
* Return to Hero's Alliance to claim contract and pick up another. I anticipate they will go after the dragon.
* If it's the dragon, they will find a solo silver dragon wyrmling who is non-combative and lawful good. If unprovoked, she will aid the party.
* Party will hopefully redeem snail mail license.

**Occurred**

* The party descended on the Temple of Purpose in an effort to clear this holy site of the bandits that recently overtook it.
* They had a brush with fate as Skagdun nearly perished in confronting a set of guards.
* After recuperating, the party returned to the open air cathedral to enter into the bowels of the site, presumptively approaching the hostage priest. 

---

### 06/27

#### Previous Summary

NA

#### Game Dates
* **Start:** 3rd day of Kythorn (The Time of Flowers)
* **End:** 3rd day of Kythorn (The Time of Flowers)

#### NPCs Present
* Farmer

#### Location(s)
* Hero's Alliance
* Wonky Donkey

#### Session Events
* On their journey to Holworth to take part in this era of magical awakening, the party came across a farmer’s plot and fought a collection of wolf spiders.
* Upon victory, the party conferred with the Farmer receiving a Hero's Alliance contract he had open, a Beacon license to be activated at the Snail Mail office, and the ArcReader. Ashitaka provided a tender offering of a love pillow to the farmer.
* After venturing to Holworth, the party briefly stopped by the Wonky Donkey for a drink and then traveled to claim their contract and join the Hero's Alliance.
* The party set out to complete contract #1 and ended the session outside the holy site.

---

### 0

My job as DM:

* Success as a DM
    + is delivering narrative depth, game realism, and player reward through process. Winning does not take a binary form in DnD. Those can be player goals as well. 
* Specifics of my job as DM
    + I am the god of this world, but my purpose is to be an impartial narrator and referee. When I use discretion, it will always be in the larger interest of the above stated goals.
    + There will routinely be game knowledge I need but don't posses in the moment. As a result, I will be constantly thinking of the cost-benefit of how difficult it would be to address the lacking info. If it's prohibitive, I will make a judgement and note I need to clarify post-session.
* I will generally be hands off.
* The story may be fragmented.
    + and things may feel clunky and we may ultimately never complete major arcs. My job is to guide the game in a manner that is adaptive to the direction, momentum, and needs of the party.

Your job as players:

* Participate in the creation of the world.
    + There are times I may call on you to do this. There are times you will be totally unaware your actions spurred unplanned events. You are just as vital as the DM to the creation of the narrative.
* Embrace the suspension of disbelief.
    + Avoid metagame awareness by compartmentalizing knowledge and working through mechanisms that make sense for your char.
* Personify your char as much as possible.
    + Aim for maximum cognitive immersion. DnD is unique in the level of mental access you have to connect with and guide the actions of a char. Strengths are obviously emphasized, but flaws hold relevance too.
* Cheating or buffing gameplay holds no value.
    + Meaningful party outcomes, good or bad, are where success is had. As the players of dwarf fortress say, "losing is fun". Get out of the "beowulf" mindset (success is automatic and always assumed).
* Cheating in-character definitely holds value
    + but it should make sense. For instance, a CN type would be out of character only doing good natured things. Steal from the party, murder every hobo, just do it with broad consideration for relevance and impact.
* Talking about success
    + it includes the thoughts and preferences of each party member. If something makes you uncomfortable, if there is an aspect of game play you'd like to see elevated or diminished, raise these issues as we go.

---

## Tools

### Tables

* [DM Tables](https://dungeonmastertools.github.io/)
    + Player ref sheet
    + Treasure tables
    + Magic Items tables
    + Travel
* [donjon](https://donjon.bin.sh/5e/)
    + Spell sheet
    + Enc table
    + Shop generator
    + Dungeon generator

### PCs

* [Ashitaka](https://www.dndbeyond.com/characters/30354523) (Chang)
* [Dimaya Urtac](https://www.dndbeyond.com/characters/30130370/FlOc6M) (Olson)
* [Sk&auml;gd&umacr;n](https://www.dndbeyond.com/characters/30600024/vTJOE5) (Skoglund)
* [Uzi Soggybottom](https://www.dndbeyond.com/characters/30350744/bpyqUe) (Gervais)
* [Vaer&uuml;ne](https://www.dndbeyond.com/characters/29959151/Hd5Mwh) (Spaeth)

### Table top

* [Discord Server](https://discord.com/channels/717564296434810890/717712797881991259)
    + This server will provide several channels to organize party communication and in-game reference distribution.
* [Combat theater](https://shmeppy.com/) (Schmeppy)
    + On the ground, tactical game play will take place in this app.

### Books

* [DMG](/home/chris/Seafile/library/personal/hobbies/dnd/refs/books/Dungeon \Master's \Guide.pdf)
* [PHB](/home/chris/Seafile/library/personal/hobbies/dnd/refs/books/Player_s \Handbook.pdf)

### Avrae Aliases

* background
* class
* classfeat
* condition
* date
* feat
* generate
* item
* monster
* race
* racefeat
* rule
* spell
* sane
* token
* weather

---

## Chars

### UA NPCs
* **Elfs**: Arbelladon Yinwarin , Ailas Omajyre , Alluin Balmys , Theodred Aralana , Taleasin Vasandoral , Gormar Farbalar , Ornthalas Virjyre , Nesterin Triswarin , Volodar Sylbella , Zaos Josatra
* **Dwarf**: Darendrog Metalstone , Skobrouth Keggrog , Varfulir Forgebuckle , Darefoid Steelbane , Huvouth Thunderforged , Vomdag Lavamaul , Nolgrarlug Shattermaul , Ararril Chaosshoulder , Joded Anvilbringer , Gotrad Snowview
* **Dragon**: poidhi, the Life Giver , tiorvaen, Protector of the Weak , chaervorth, the Gifted , bieperth, the Jealous One , tudhait, the Dark , dennian, the Puny , gaekae, the Tall , payvinteil, the Bunny Killer , xudaepheo, the Warm , uvirus, the Dragonlord
* **Dragon**: micdic , iktec , gosuph , krecshu , baizax , grona , roldrebuph , rocdraelo , velarciks , hoshiroz
* **Human**: rishun cinom , bhurad cukhen , birkudd Fourclaw , nibrork Silentbelly , mabram ven , kem navrosk , golvor Roughbow , murth Voiddrifter , thehvezuz michahkem , dinas muuhreft , temondesk netrotvurgu , zirlat vruvzako , ioy li , jiap chuen , uerdeanez zascudrul , venin paldurgel

* **Onry**: Human Bard, strong sense of nationalism.
* **Loby Finell**: Female Halfling Paladin, Good. Str 15, Dex 8, Con 7, Int 11, Wis 14, Cha 16. Loby has a round face, with golden hair and brown eyes. She wears splint armor and wields a warhammer and shield.
* **Arget Courte**: Female Halfling Mercenary, CG. Str 10, Dex 12, Con 6, Int 13, Wis 10, Cha 15. Arget is tall and willowy, with auburn hair and soft gray eyes. She wears leather armor and wields a shortsword.
* **Threri**: Male Dwarf Cleric, NG. Str 9, Dex 12, Con 11, Int 9, Wis 15, Cha 15. Threri has blonde hair and hazel eyes, and a curly moustache. He wears hide armor and wields a light hammer. Threri seeks to discover the truth of his lineage.
* **Amira**: Female Halfling Peasant, NE. Str 10, Dex 9, Con 11, Int 9, Wis 8, Cha 9. Amira has thin gray hair and narrow brown eyes, and large ears. She wears simple clothing and carries a long knife. Amira is envious and deceitful.
* **Hildga**: Female Dwarf Ranger, N. Str 8, Dex 10, Con 12, Int 12, Wis 13, Cha 8. Hildga has cropped golden hair and gray eyes. She wears half plate and wields a whip and shield. Hildga is extravagant and fierce.
* **Ancin Gere**: Male Human Merchant, NG. Str 10, Dex 11, Con 10, Int 10, Wis 11, Cha 8. Ancin has thin red hair and blue eyes. He wears modest garments and a blue cloak. Ancin has an animal companion, a black cat named Ethen.
* **Zita**: Male Half-orc Priest, NG. Str 8, Dex 10, Con 9, Int 11, Wis 12, Cha 12. Zita has copper hair and blue eyes, and prominent ears. He wears well-made clothing and carries a fine stiletto. Zita secretly serves Kaveph, an ancient god of chaos.
* **Thrica**: Male Half-orc Alchemist, N. Str 9, Dex 6, Con 13, Int 10, Wis 14, Cha 8. Thrica has a narrow face, with blonde hair and bright green eyes. He wears well-made clothing and a sling of vials and potions. Thrica seeks revenge against the sister who betrayed him.
* **Ursas**: Female Gnome Scofflaw, NG. Str 8, Dex 10, Con 12, Int 11, Wis 11, Cha 10. Ursas has auburn hair and sharp amber eyes, and pointed ears. She wears sturdy clothing and several pouches hang from her belt.
* **Staga Jornidotr**: Female Dwarf Merchant, LN. Str 10, Dex 12, Con 12, Int 6, Wis 11, Cha 6. Staga is rough in appearance, with white hair and soft brown eyes. She wears plain clothing and a wide-brimmed hat. Staga has an animal companion, a gray rabbit named Bifar.

### Leo Ferrari
* **Race:**
* **Class:**
* **Motivations:**
* **Traits:**
* **Location:**
* **Background:**

### Prahmethoth
* **Race:** Alhoon
* **Class:**
* **Motivations:**
* **Traits:**
* **Location:**
* **Background:**

### Farmer
* **Race:** Human
* **Class:** Fighter
* **Motivations:** Live a simply after a life of adventuring
* **Traits:** old, feeble
* **Location:** Farm off main road south of Holworth.
* **Background:** Spent a career as an adventurer with wife but has since retired.

### W. Fitzhugh Brundage
* **Race:**
* **Class:**
* **Motivations:** discovery, aid the party in pursuit of discovery, support Progenitor Trust
* **Traits:** intelligent, curious, persistent
* **Location:** Threapnalt University
* **Background:**
    + Conducts academic work on the arcane.
    + Stands as a leader in the early findings of arcane mechanisms (Ves-Tonder System).
    + Currently expanding into area of esoteric drift.
    + Is an active member of the Progenitor Trust.

### Mule
* **Race:**
* **Class:**
* **Traits:** feeble, psyonic abilities, appears to be harmless
* **Motivations:** serve Prahmethoth as main lieutenant
* **Location:**
* **Background:**

### Siyorac
* **Race:** Human
* **Class:** Guard
* **Traits:**
* **Motivations:** Serve Aldock
* **Location:** Holworth South Gate
* **Background:**

### Laquillal
* **Race:** Orc
* **Class:** Barkeep, commoner
* **Traits:** Non-binary, energetic
* **Motivations:** Serve good beer
* **Location:** Wonky Donkey
* **Background:** Laquillal is the barkeep of the Wonky Donkey.

### Asarkal
* **Race:** Human
* **Class:** Warlock
* **Traits:** loyal, organized
* **Motivations:** Serve with dignity
* **Location:** Holworth Hero's Alliance
* **Background:** Asarkal is the commander of the Holworth HA branch.

### Baizax
* **Race:** Silver Dragon
* **Class:** Wyrmling
* **Motivations:** Follow a drive for exploration. Maintain a deep conviction of honor. Support the efforts of a great cause. Defend the innocent.
* **Traits:** lawful good, curious, honorable
    * prominent neck frills, a beaklike snout, plated facial armor, and long, backswept horns. From a distance, the exceptionally fine scales appear to blend together, lending the dragon the appearance of a sculpture
    * scent reminiscent of rain and evergreen needles
* **Location:** Lair of Baizax
* **Background:** Approximately a 4yo silver dragon

---

## Encounters

puzzle ideas

* poem that is a for loop to complete task
* backward wall - wall appears when party turns around. Cryptic inscription indicating they need to walk backward to go forward
* rude door
* items disappear, task completed without equipment
* prisoners dilemma - players enter room where they respectively enter visual\/audio cones of isolation. must figure out dynamic collectively to solve puzzle
    + players role covert int saves
    + split party in half to separately meet the king
    + king explains they've been selected for their intellectual and strategic prowess and brought to his "strategic plane" (think of better term for situation room)
    + king states he is in need of guidance on how to spend resources in his kingdom for the next 3 yrs relative to his neighboring rival
    + he can invest in his kingdom or go to war
    + should he prepare for peace or prepare for war
    + players receive payment for lucrative guidance and punishment for lopsided outcomes.
* pc performs action to bind themselves to curse, they get isolated, a simulacrum of that pc returns to the party to fight them
* hoffman encoding for Prahmethoth encrypted messages
* graph algorithm
* timed effects
* kobe - party needs to cast fireball through basketball hoop
* https:\/\/docs.google.com\/document\/d\/1hfompGbslrV_YvQ4ktPnY7vg-_blkIZ72hPcXLEWZdQ\/edit

---

## Organizations

### Round Earth Society
* **Description:** An advocacy group that promotes the belief the world is spherical while denying existence of a firmament.
* **Mission statement:**
* **Motto:** We're ahead of the curve.
* **Goals:** Promote the belief that the world is spherical.
* **Location:**
* **Services:**
* **Membership:**
* **NPCs:** Leo Ferrari
* **Story arcs:**
* **Background:** This group is one of many elements who have embraced psuedointellectual leanings in the wake of the Awakening. The degree to which society's understanding of reality was fundamentally changed has uprooted many previously steadfast beliefs.

### Progenitor Trust
* **Description:** An order of Verdan mages who, previously beset by oppression, heavily embraced magic post-[awakening].
* **Mission statement:**
* **Motto:**
* **Goals:** Employ academic head start in magic prowess to organize a coup. Upon seizing power, embark on aggressive conquest in expansion of race influence.
* **Location:** Threapnalt University
* **Services:**
* **Membership:**
* **NPCs:**
    + W. Fitzhugh Brundage
* **Story arcs:**
    + Realignment
* **Background:** The race are a people who have historically been oppressed by the ruling class of their locale. In the immediate aftermath of the [awakening], the race made early investments in magical knowledge and building of their collective capability. A race previously beset with little opportunity saw dramatic advancements in the state of their human capital. Even still, this did not come with social realignment, and thus, the leadership of the race have set out to correct this historic imbalance.

### Emerald Compact
* **Description:** Underground, decentralized eco-terrorist group that utilizes militant tactics in limiting humanoid environmental impact.
* **Mission statement:**
* **Motto:** The earth laughs in flowers
* **Goals:**
    + Enlists agents to support their cause of environmental intervention.
    + Coordinate efforts to obstruct humanoid causes of environmental damage by any means necessary.
    + A primary target of their focus is the recent expansion in mining for magical ore.
* **Location:** Unknown
* **Services:**
* **Membership:**
    + Allegiance is sworn upon receiving an invitation to become an agent.
    + Agents are conscripted to secrecy.
    + All druids are given an opportunity at membership.
* **NPCs:**
* **Story arcs:**
* **Background:**

### Hero’s Alliance
* **Description:** A union of adventuring members with common goals and public professional services.
* **Mission statement:**
* **Motto:** I wish to see what lies beyond
* **Goals:**
    + Provide public access to adventurer talent and services through contract hire.
    + Serve as support union for adventurers.
    + Give endless feed of easy quest plot hooks.
    + Remain apolitical.
* **Location:** Branches in most major cities.
* **Services:**
    + Contract to hire adventurer jobs
    + Training
    + Practice combat theater
* **Membership:**
    + Must be actively working as a professional adventurer.
    + Complete a test job at discretion of branch warden
* **NPCs:**
* **Story arcs:**
    + An introduction
* **Background:**

### Snail Mail
* **Description:** Aldock Distributed Messaging Brokerage. A communication service of the flail snail hive mind collective. AKA Snail Mail.
* **Mission statement:**
* **Motto:**
* **Goals:** Provide high fidelity messaging services across the realm.
* **Location:** Branches in most major cities.
* **Services:**
    + Priority Telepathy –
    + Priority Express Telepathy -
    + Beacon License – recipients receive charm which allows for persistent tracking in roaming message delivery.
    + Joke payment – flail snails love jokes. A new joke (and food) can substitute as payment for a received message.
* **Membership:**
    + Standard pricing array for varying services
    + Certain Licenses that allow for elevated access and pricing gratuity
* **NPCs:** flail snail hive mind collective
* **Story arcs:** An introduction
* **Background:** Flail snails take their service to the realm very seriously. Their collective psionic capabilities allowed them to provide their services long before the [awakening] and the introduction of other methods of arcane data transfer.

### Threapnalt University
* **Description:** An institution of higher learning in the arcane arts
* **Mission statement:**
* **Motto:** Driven to Discover
* **Goals:** Advance the discovery of arcane knowledge.
* **Location:** Holworth, Noon Orchard district
* **Services:**
    + Library
    + Training
* **Membership:**
    + Admissions process for students
    + Hiring process for faculty
* **NPCs:**
    + W. Fitzhugh Brundage
* **Story arcs:**
    + Main plot
    + Realignment
* **Background:** Named for founding leader of Progenitor Trust.

---

## Places

### Wonkey Donkey
* **Location:** Holworth, Stormgrove dist
* **Description:** Energetic atmosphere
* **NPCs:** Laquillal
* **Organizations:**
* **Items:**
* **Story arcs:**
* **Background:**

### Holworth Hero's Alliance
* **Location:** Holworth, Applearch
* **Description:**
* **NPCs:** Asarkal
* **Organizations:**
* **Items:**
* **Story arcs:**
* **Background:**

### Temple of Purpose
* **Location:** Just off the lesser route, 5mi S of Chilseading
* **Description:**
    + *Map:*
    + An open air regional holy site of the Witnesses of Morinzi.
    + The site features a large assembly platform that centers on a lecturn and the main feature of an eternal flame.
    + Additionally, there is an underground structure that serves as an organizing and worship environment for the religious leadership.
* **NPCs:**
* **Organizations:** Witnesses of Morinzi
* **Items:**
* **Story arcs:** HA contract #1
* **Background:** Built about 400 years ago, this eternal flame just outside the city limits is here to celebrate the rich musical and artistic history of this region, which is still part of it today. Its position within this community is meant to represent the heart and soul of the people and the unbreakable bond between past and future generations. It was designed by a famous international artist who accurately captured the varied history of the region and used an elegant style to convey her vision in this piece of art.  Every element was crafted and created with durable materials from local suppliers, ensuring this monument will continue to adorn the community for generations to come.

### Lair of Baizax the Wyrmling
* **Location:** Upstream of the Dunter River, W of Holworth near small burough of Brushgathershire
* **Description:** A small cave network with a large central cavern where Baizax has settled in.
* **NPCs:** Baizax the silver dragon wyrmling
* **Organizations:** NA
* **Items:**
* **Story arcs:** HA contract #7
* **Background:** Cavern was unoccupied prior to Baizax taking up temporary shelter here. The cave is fille with typical cavern vermin otherwise.

### Brushgathershire

* Brushgathershire is a primarily Halfling village with a population of 313. The population is 86% halfling, 1% human, 1% elf, 1% dwarf, and 11% other races.
* Public Figures:
* Mayor: Alton Tosscobble, Halfling
* Greeter: Verna Tealeaf, Halfling
* Guard Captain: Portia Fingertoes, Halfling
* Religious Leader: Wellby Tosscobble, Halfling
* Town Gossip: Vani Tosscobble, Halfling
* Tavern
    * Name: Sapphire Crocodile
    * Owner: Milo Greenbottle, Halfling
* Most Popular Smith
    * Name: Andry's Smithy
    * Owner: Andry High-hill, Halfling
* Tailor
    * Name: Modern Raiments
    * Owner: Wellby Tosscobble, Halfling
* Bakery
    * Name: Hot Pastries
    * Owner: Paela Greenbottle, Halfling
* Most Popular Butcher
    * Name: Exalted Meatmarket
    * Owner: Eldon Thorngage, Halfling

---

## Story arcs

https://docs.google.com/document/d/1ADbrYtsI6_EhYRgBtzKQB1Iv4TgbouZfLKV7YRU2XeM/edit

With esoteric drift:

* The realm lacks magical properties due to an arcane energy void
* BB identifies the value of this to advance arcane study and avoid elder brain detection while pursuing motivations
* BB discovers method to manipulate esoteric drift that fills arcane void, making interaction with the weave possible
* Need: ability or artifact to manipulate esoteric drift.
* This artifact/ability gives BB ability to conduct work in synthesized arcane space, effectively turning magic on/off. Goal is to achieve some kind of immortality without elder brain (lichdom, divinity)
* Party can discover method of controlling ability or forging artifact to give esoteric drift permanence.

subplots

political factions of mage guild

* order of thieves - secretly enlist party thief as plot mechanism
* construct experimentation methodology as mechanism for puzzle solving
* create historian character to provide exposition on discovery of magic
* create university and academic chars to provide exposition on magical properties
* subjugated race embraces magic early and forms strong fabric within magic community at heart of country where magic is introduced. they intend to over throw their oppressors and embark on aggressive conquest.
* radical environmentalist group forms and enlists agents to support their cause of intervention
* mining for magical ore has expanded dramatically
* [world name] distributed messaging brokerage - A service of the flail snail hive mind collective. party receives credentials for premium beacon \"tracking\" service. snails take payment in food or jokes.
* create npc modeled after the mule. feeble, psyonic abilities, appears to be harmless. maybe is main lieutenant for Prahmethoth
* gods converge on the reintroduction of magic, sending heralds and trying to vie for control of \"fresh\" territory.
* arms manufacturer offers lucrative contract to party

### Cows in the village

### HA Contracts

#### Active
2. A monster is making travel dangerous to the NE.
    + Obj: Eliminate monster. Return with proof.
    + Pay: 100gp
3. A local smith is experiencing daily vandalism.
    + Obj: Stand watch for night to deal with vandals.
    + Pay: 125gp, use of shop
4. A territorial dispute between merchant guilds has led to bouts of violence.
    + Obj: Mediate terms. Address any non-compliance.
    + Pay: 300gp
6. The activity of a kobold stronghold has begun to encroach on the neighboring hamlet.
    + Obj: Clear stronghold. Destroy any stronghold infrastructure.
    + Pay: 225gp
7. A dragon hatchling has been discovered in the countryside.
    + Obj: Venture to its nest and eliminate it before it becomes a major liability
    + Pay: 150gp
8. A noble is in need of an escort.
    + Obj: Act as guide and defense for noble's detail
    + Pay: 300gp

#### Pending
9. A mining operation is experiencing insurrection among its workforce.
    + Obj: Infiltrate the operation and eliminate sedition leadership.
    + Pay:
10. Recent evidence of an assumed lost family heirloom has surfaced.
    + Obj: Confer with client, and retrieve item.
    + Pay:
11. Something with the university
12. Join a banner to fight in Challenger Gauntlet

#### Completed
1. Bandits have overrun a nearby holy site and captured priest.
    + Obj: Clear the site, and free priest.
    + Pay: 200gp
5. A farmer outside of town is experiencing a giant wolf spider infestation.
    + Obj: Inspect property, and eliminate the spiders.
    + Pay: 50gp

### A Titan's Price
* **Outline:**
    + *Event:* Prahmethoth introduces magic to realm.
    + *Impact:* After millennia without arcane magic, this world undergoes a dramatic technological awakening.
    + *Call to action:* Inconsistencies in magical fidelity and a growing presence of Prahmethoth's work begin impacting society.
    + *Turn:* Upon initial confrontation, the PCs learn Prahmethoth has granular control of esoteric drift, rendering him virtually invincible.
    + *Resolution:* The PCs attempt to develop a method for esoteric permanence, allowing them to fight Prahmethoth at full strength.
* **Exposition:** This world is a lost Plagueland where a fundamental connection with the weave is broken. Due to unknown effects, esoteric drift dynamics have effectively created an arcane energy void. All mechanics of the Ves-Tonder system are intact but cannot function with the energy vacancy. While attempting to attain a level of divinity, the Alhoon Prahmethoth travels to this realm in an effort to avoid detection from the Elder Brain. Through his work, he discovers a method to manipulate esoteric drift. This enables the draw of arcane energy to this space, effectively introducing the completed circuit of the weave to the realm.
* **Items:**
* **Chars:**
    + Prahmethoth
* **Plot hooks:**  
* **Events:**
    + Anticipated:**
        - "blackout" event where magic shuts off momentarily. Prahmethoth is testing something that impacts esoteric permanence.
    + Transpired:**

### Heralds Inbound
* **Outline:**
    + *Event:* gods converge on the reintroduction of magic, sending heralds and trying to vie for control of "fresh" territory.
    + *Impact:*
    + *Call to action:*
    + *Turn:*
    + *Resolution:*
* **Exposition:**
* **Items:**
* **Chars:**
* **Plot hooks:**  
* **Events:**
    + Anticipated:**
    + Transpired:**

### An Introduction
* **Outline:**
    + *Event:* PCs appear and witness farm being attacked.
    + *Impact:* Risk of harm to everyone in area.
    + *Call to action:* Only the party can save the farmer.
    + *Turn:* Party decides to intervene.
    + *Resolution:* Farmer is grateful and passes on prized adventuring items
* **Exposition:** The PCs were drawn to Holworth as the cultural epicenter of magic. The farmer is a former adventurer and will pass on his items if assisted.
* **Items:** ArcReader, Snail Mail beacon license, Hero’s Alliance contract
* **Chars:**
    + Old farmer
    + Attacking giant wolf spiders
* **Plot hooks:**  NA
* **Events:**
    + Anticipated:**
        - Random encounter with aggressor NPCs
        - Party intervenes to save farmer
        - Party carries on to investigate leads from items they received
    + Transpired:**

### Realignment
* **Outline:**
    + *Event:* The Progenitor Trust attempts to organize a coup and seize power within their locality.
    + *Impact:* With their early investments in magical capability, the Trust is able to upend the historical power structure and seek greater ambitions (conquest).
    + *Call to action:* 1) Gain sympathy of party and participate in the coup. 2) Prevent coup.
    + *Turn:* 1) Party becomes aware of intentions beyond coup
    + *Resolution:* Party succeeds in either C2A they choose.
* **Exposition:** The race are a people who have historically been oppressed by the ruling class of their locale. In the immediate aftermath of the [awakening], the race made early investments in magical knowledge and building of their collective capability. A race previously beset with little opportunity saw dramatic advancements in the state of their human capital. Even still, this did not come with social realignment, and thus, the leadership of the race have set out to correct this historic imbalance.
* **Items:**
* **Chars:**
* **Plot hooks:** 
* **Events:**
    + Anticipated:**
        - Party interacts with race leadership.
        - Blackout creates window for local leader to raid race hq.
        - Coup succeeds and race installs new power structure.
        - Race begins expansion of forces in effort to embark on aggressive conquest
    + Transpired:**

### Arms Race
* **Outline:**
    + *Event:* arms manufacturer offers lucrative contract to party
    + *Impact:*
    + *Call to action:*
    + *Turn:*
    + *Resolution:*
* **Exposition:**
* **Items:**
* **Chars:**
* **Plot hooks:**  
* **Events:**
    + Anticipated:**
    + Transpired:**

### Twin Metals
* **Outline:**
    + *Event:* mining for magical ore has expanded dramatically
    + *Impact:*
    + *Call to action:*
    + *Turn:*
    + *Resolution:*
* **Exposition:**
* **Items:**
* **Chars:**
* **Plot hooks:**  
* **Events:**
    + Anticipated:**
    + Transpired:**

---

## Things

ArcReader, Snail Mail beacon license

