---
title: "![](armour.svg) Mead Hall"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: readable
---

```{r global_options, include=F}
knitr::opts_chunk$set(eval=F)
```

```{r eval=F, include=F}
# Dependencies

library(rmarkdown)
library(knitr)
```

### Weekly Recap {.tabset .tabset-fade}

#### *

---

World Building

## Places
### ENTRY
* Location:
* NPCs:
* Organizations:
* Background:
* Items:
* Story arcs:
* Description:

## Chars
### ENTRY
* Traits:
* Motivations:
* Background:
* Location:

## Things
### ENTRY
* Item qualities:
* Background:
* Location:

## Story arcs
### ENTRY
* Outline: 
    + Event:
    + Impact:
    + Call to action:
    + Turn:
    + Resolution:
* Further exposition:
* Primary chars:
* Events: anticipated, transpired:
* Plot hooks:  

## Encounters
### ENTRY
* Dungeon map: 
* Location:
* Weather:
* Environment:

## Organizations
### ENTRY
* Mission statement:
* Motto:
* Goals:
* Background:
* Location:
* NPCs:
* Story arcs:

Session log

Action summaries
