---
title: "![](armour.svg) Mead Hall"
output:
  html_document:
    theme: readable
---

```{r global_options, include=F}
knitr::opts_chunk$set(eval=F)
```

```{r eval=F, include=F}
# Dependencies

library(rmarkdown)
library(knitr)
```

### Weekly Recap {.tabset .tabset-fade}

#### 12/13
* A pleasant rest brought daylight and the awareness of movement along the rode from Greenbottle Hill. Upon inspection by Skagdun, it became clear a militia of locals had been assembled in response to the party's actions.
* With a set of fern hounds in tow, the militia was on the hunt. A brush with the senses of the hounds initiated near contact that was only delayed with a scented candle-based diversion. Still, at the hounds beckon, the militia detected they were closing in, and a loose chase ensued.
* The party moved with haste, leveraging the ranging tactics of Skagdun and maneuvering of Vaerune to arrive in the hamlet unaware of the degree of their safety. A search for shelter led to the pub and their acquaintance, Leo Ferrari. Leo welcomed the party with dramatic affection after initiation into the Round Earth Society.
* Leo's home and lab were found to be a domicile characteristic of his personality, although still filed with a genuine sincerity. Through Leo's efforts, the party evaded detection all while learning about Leo's unexpected heritage.

#### 11/21
* At the outset, confrontation. Dimaya successfully captured the attention of Samuta while in pursuit, attempting to avoid violence.
* In a tense exchange, the party learned Samuta was taken as a hatchling and enslaved by Nidei. The two of them seem to be callous entrepreneurs that are serving a lucrative contract applying their method of cold iron synthesis. Additionally, a vague reference was made to the retrofitting of military armaments.
* The party attempted to negotiate their presence in the mine but was unable to sway the pair, and Nidei insisted on confronting their mutual employer.
* Fortunately though, the party was offered a window of escape as a plume of smoke made the fire apparent to Nidei.
* The party took flight but realized they were leaving an unraveling situation with lingering consequences. A good deal of deliberation led to the conclusion they needed to silence their potential betrayers.
* In separate confrontations - Samuta through serpentine force and Nidei through parler tricks - the pair attempted to overpower the returning party with no success. Samuta met her demise while Nidei was able to escape and remain at-large.
* With a quagmire growing in dimension at every step, the party elected to lay low and assess the fall out.

#### 11/5
* Venturing deeper into the mine, the party came across further outfitting in the development of the operation.
* The party also reflected on the assumed goals of the operation and how cold iron might fit into the picture.
* Uzi recalled hearing somewhere that cold iron has efficacy against fey creatures, though it's speculated this includes other races given the recency of magic material use in smithing.
* After exploring a cache and excavation site, a fire was started around large portions of smelting implement.
* To avoid the fire, the party chose another wing of the mine where they discovered an old wizard and a white dragon wyrmling utilizing frost magic in processing ore.
* Ashitaka attempted to approach the pair unnoticed without success. In a rush of panic, the party fled, initiating a chase and an intense encounter.

#### 10/29
* The party continued through the mine that was seemingly abandoned by any civilized creatures. Instead the party encountered several natural dwelling inhabitants during their exploration.

#### 10/11
* After being returned to their camp, the party proceeds to make sense of their circumstances by looking for LL and Onry.
* Skagdun conducts a brief search to find the pair sitting, motionless, in a nearby clearing. When prompted they seem totally unaware of anything that transpired.
* Unable to make sense of these events, they continue on to eventually arrive at the mine where the party is told not to enter.
* The party then travels to the nearby hamlet of Greenbottle Hill to investigate some info divulged by Onry re a wizard associate of LL.
* While at a tavern Dimaya reaffirms her stance of the widely known fact that the world is flat.
* Without much conclusive intel, the party decides to enter the mine in aggressive fashion.

#### 09/20
* After the confrontation with what were assumed to be agents of the terrorist group, the Progenitor Trust, the party found themselves in a sort of pocket dimension.
* The space was a setting with features not unfamiliar from their home plane but was clearly defined magical parameters.
* With a variety of clever problem solving, the party identified several lock-and-key steps to freely pass through stages of the pocket dimension.
* When they finally aided in a king's dilemma, they were released back to their home plane - some having been rewarded, others punished.

#### 08/23
* The party continued their trek toward the Laurentz Mine as they left the well-traveled road past Marwark and entered dense wilderness.
* The caravan encountered several events of intrigue and intensity - a parlay with a band of gypsies, encroaching on a drake's territory, and a bout with some quicksand.
* In exploring a camp site, Skagdun discovered a symbol which Onry identified as the mark of the Progenitor Trust, a Holworth-based terrorist group.
* They attempted to avoid a confrontation to no avail. While Uzi stood watch, the camp was attacked by 3 hooded figures who swiftly transported the party to an unfamiliar place.


#### 08/16
* The party accepted another HA contract that will take them through the wilderness at the behest of a local noble business leader.
* In initiating this contract, the party met Lady Luna Laurentz and her CoS, Onry. They set out west toward the mine, first traveling down the road toward Marwark.
* During this leg of the journey, the party discovers they are being tracked by a lone Orog who they ambush and dispatch with some effort.


#### 07/26
* The party continued through the administrative center of the Temple of Purpose, clearing the site and finally confronting the Bandit Captain that had taken the priest hostage.
* After freeing the priest, he made the party aware that the eternal flame in the proscenium was the site of a miracle, bestowing healing powers. Additionally, the priest used a scroll to endow the entire party with inspiration.
* The party then returned to the Holworth HA to claim their contract and pickup a new one

#### 07/12
* The party descended on the Temple of Purpose in an effort to clear this holy site of the bandits that recently overtook it.
* They had a brush with fate as Skagdun nearly perished in confronting a set of guards in the outdoor proscenium.
* After recuperating, the party returned to the open air cathedral to enter into the bowels of the site, presumptively approaching the hostage priest. 

---

#### 06/27
* On their journey to Holworth to take part in this era of magical awakening, the party came across a farmer’s plot and fought a collection of wolf spiders.
* Upon victory, the party conferred with the Farmer receiving a Hero's Alliance contract he had open, a Beacon license to be activated at the Snail Mail office, and the ArcReader. Ashitaka provided a tender offering of a love pillow to the farmer.
* After venturing to Holworth, the party briefly stopped by the Wonky Donkey for a drink and then traveled to claim their contract and join the Hero's Alliance.
* The party set out to complete contract #1 and ended the session outside the holy site.

---

#### 0
My job as DM:

* Success as a DM
    + is delivering narrative depth, game realism, and player reward through process. Winning does not take a binary form in DnD. Those can be player goals as well. 
* Specifics of my job as DM
    + I am the god of this world, but my purpose is to be an impartial narrator and referee. When I use discretion, it will always be in the larger interest of the above stated goals.
    + There will routinely be game knowledge I need but don't posses in the moment. As a result, I will be constantly thinking of the cost-benefit of how difficult it would be to address the lacking info. If it's prohibitive, I will make a judgement and note I need to clarify post-session.
* I will generally be hands off.
* The story may be fragmented.
    + and things may feel clunky and we may ultimately never complete major arcs. My job is to guide the game in a manner that is adaptive to the direction, momentum, and needs of the party.

Your job as players:

* Participate in the creation of the world.
    + There are times I may call on you to do this. There are times you will be totally unaware your actions spurred unplanned events. You are just as vital as the DM to the creation of the narrative.
* Embrace the suspension of disbelief.
    + Avoid metagame awareness by compartmentalizing knowledge and working through mechanisms that make sense for your char.
* Personify your char as much as possible.
    + Aim for maximum cognitive immersion. DnD is unique in the level of mental access you have to connect with and guide the actions of a char. Strengths are obviously emphasized, but flaws hold relevance too.
* Cheating or buffing gameplay holds no value.
    + Meaningful party outcomes, good or bad, are where success is had. As the players of dwarf fortress say, "losing is fun". Get out of the "beowulf" mindset (success is automatic and always assumed).
* Cheating in-character definitely holds value
    + but it should make sense. For instance, a CN type would be out of character only doing good natured things. Steal from the party, murder every hobo, just do it with broad consideration for relevance and impact.
* Talking about success
    + it includes the thoughts and preferences of each party member. If something makes you uncomfortable, if there is an aspect of game play you'd like to see elevated or diminished, raise these issues as we go.

---

