---
title: "![](armour.svg) World"
output:
  html_document:
      toc: yes
      toc_float: yes
      theme: readable
---

```{r global_options, include=F}
knitr::opts_chunk$set(eval=F)
```

```{r eval=F, include=F}
# Dependencies

library(rmarkdown)
library(knitr)
```

---

## Chars

---

### Ashitaka (Chang)

* Class: Paladin
* Race: Dragonborn
* Skill Rolls: 15, 14, 13, 12, 10, 8

#### Niche

Tank

#### Background

History:
I grew up in a remote village of dragonborns, and I was chosen to be a holy soldier for Sirrion. I was tantalized by the stories of passing merchants and travelers, and I dreamed of going on a grand adventure. My curiosity and distain for commands often landed me in trouble with the elders of the tribe. I always questioned the reasoning behind my duties, and I often disobeyed. At 13, I refused an order to execute a villager who had been accused of heresy. The Church of Sirrion ex-communicated me, and I was banished from the tribe. I embarked on my grand adventure to seek freedom and to defend the oppressed.

Background: Outlander

Origin: Outcast

Personality trait: I value my personal freedom the most, and every action I take is on my own volition. I detest oppressors and love new and interesting people.

Ideal: Change. Life is like the seasons, in constant change, and we must change with it.

Bond: I seek to free and protect those bounded by physical or metaphorical chains.

Flaw: Large crowds and tight spaces give me anxiety, and I am easily enticed by slabs of meat.

#### Goals

Have fun, learn new things, and meet new people

---

### Dimaya (Olson)

* Class: Sorcerer
* Race:
* Skill Rolls: 18, 12, 10, 13, 11, 16

#### Niche

Spellcaster/jack-of-all-trades since I have some experience playing

#### Background

Hermit/outlander of some sort, someone from the wilderness

#### Goals

On a sort of quest of self-discovery, maybe a pilgrimage or something similar

---

### Uzi Soggybottom (Gervais)

* Class: Monk
* Race:
* Skill Rolls: 12, 13, 11, 10, 16, 17

#### Niche

One for the people.  I will always do what is best in order to benefit the group.

#### Background

Trained in monastery until the age of 12 when a catastrophic storm hit the civilization where the monastery was located killing off all forms of life.  Miraculously Uzi survived.  With all belongings, food, and clothing gone Uzi scrambled to survive.  He stumbled upon colony of albino dwarves that looked to have food, clothing, and money.  Uzi attempted to steal what he needed from a local bizarre, but was captured by the local authorities, and was imprisoned.  After multiple years of imprisonment, the local albino dwarves realized that Uzi was not a dangerous threat to the community so he was released and given a job teaching Kung Fu to local dwarven folks.  Uzi had no reason to leave as he now had everything he needed to survive.  Uzi has an appetite for adventure and had an itch to explore but never the reason to leave.  Over the years, Uzi became respected within the community where the albino dwarves consider Uzi as one of their own.

#### Goals

To execute all things with complete and utter style and coolness.

---

### Sk&auml;gd&umacr;n (Skoglund)

* Class: Ranger
* Race:
  Height: 6'0"
  Weight: 180lb
* Skill Rolls: 15, 14, 13, 12, 10, 8

#### Niche

I can defend the group from shitty monsters that want to fuck up our shit. I will also help communicate with beasts of the wild and use my natural outdoorsiness to get the gang out of jams

#### Background

I'm an outlander who was cast out into the woods at a young age. My family was killed by a viscous monster and because of my halfling blood, neither the humans or the elves would take me in. I wandered the woods until a wiley, rag tag group of rangers found me and taught me their ways. Including human pleasures such as drinking, fucking, and enjoying a dabble in some of nature's many hallucinogenics. While oftentimes tempted by the money and spoils of wealthy criminals wishing us to do their nefarious bidding, we took an oath of dignity and goodness. Because of my half elf blood, I've outlived many of my mentors, but will sometimes work with the now-grown sons and daughters of my original squad who have grown up in the woods. And one day I'm going to find that monster and his bastard monster babies and fuck him up.

#### Goals

Fucking up the aforementioned monster and his bastard babies. Also, I would like to be a helpful contributor and not die in my first battle.

---

### Vaer&uuml;ne (Spaeth)

* Class: Druid
* Race: Elf - High Elf - Moon Elf (Teu-tel-quessir)
* Skill Rolls: 12, 13, 10, 10, 9, 14
* Age: 62
* Skin Color: Ice Blue
* Eye Color: Blue
* Hair Color: Dark Brown
* Height: 5’11”
* Homeland: Northwest Faerûn / High Forest / Turlang’s Wood
* Deity: Auril
* Magics: Healing / Arcane / Animal Handling
* Weapon: Shadowtop wood handled scimitars
* Animal Companion: Aüir - Displacer Beast

#### Niche

Support

#### Background

I grew up in the forests of Northwest Faerûn, but was born near Waterdeep. My mother and father served as aids to Turlang, the treant who governed the High Forests. Originating from the Feywild, they were deeply connected to arcane magics and plane of the Faerie, but were lost during the Spellplague that shattered Waterdeep in 1389. After their deaths I was taken by Turlang to be raised by dryads. I learned to shape and care for the forests and developed a strong independence in my own explorations of the forests and training. I have a strong affinity for animals and the ability to tap into the spirit of all living things and feel the balance of nature has over them. Often spending weeks or months haunting the deepest and darkest areas of the forests I have become aligned with the Circle of the Moon and am highly changeable during a full moon. While I do not yet possess full control of my shape shifting powers I have experienced times when my arcane heritage and connection to the ethereal plane of the Feywild has taken over and I have uncontrollably shapeshifted into a displacer beast. During one of these sessions I came across a displacer beast, Aüir, who I befriended. Aüir is distrustful of others, but deeply loyal to me. He often roams the Feywild when not accompanying me on my travels. He prefers my displacer beast form over that of my High Elf form so often only appears during a full moon when I become highly prone to shapeshifting into a displacer beast myself.

#### Goals

I strive for balance and harmony through the creation and conservation of living beings. I am young (for an elf) so I have a strong tendency to be independent. I challenge the betrayal of nature in any form and seek to fight those aligned with darkness.

---

### Siyorac
* **Race:** Human
* **Class:** Guard
* **Traits:**
* **Motivations:** Serve Aldock
* **Location:** Holworth South Gate
* **Background:**

### Laquillal
* **Race:** Orc
* **Class:** Barkeep, commoner
* **Traits:** Non-binary, energetic
* **Motivations:** Serve good beer
* **Location:** Wonky Donkey
* **Background:** Laquillal is the barkeep of the Wonky Donkey.

### Asarkal
* **Race:** Human
* **Class:** Warlock
* **Traits:** loyal, organized
* **Motivations:** Serve with dignity
* **Location:** Holworth Hero's Alliance
* **Background:** Asarkal is the commander of the Holworth HA branch.

### Farmer
* **Race:** Human
* **Class:** Fighter
* **Motivations:** Live a simply after a life of adventuring
* **Traits:** old, feeble
* **Location:** Farm off main road south of Holworth.
* **Background:** Spent a career as an adventurer with wife but has since retired.

### Big Bad Guy

Spooky stuff

